\newproblem{16.5a}
{
	Salto Angel (waterfalls) in Venezuela have a height of 2648 feet. A pebble is thrown upward from the top of the falls with an initial velocity of 30 feet per second. The height of the pebble after $t$ seconds is given by the equation $h=-16t^2+30t+2648$. How long after the pebble is thrown will it be 1324 feet from the ground? Round to the nearest tenth of a second.
}
{
	\begin{tabular}{l r}
	$1324=-16t^2+30t+2648$ or $0=-16t^2+30t+1324$ & 1 pt to here\\
	$t=\frac{-30 \pm \sqrt{30^2-4(-16)(1324)}}{2(-16)}$ & 2 pt to here\\
	$t=10.08238$ &  3 pts to here\\
	$10.1$ seconds & 4 pts to here\\
	\end{tabular}
}

\newproblem{16.5b}
{
	The Gullfoss (waterfalls) in Iceland have a height of 104 feet. A pebble is thrown upward from the top of the falls with an initial velocity of 25 feet per second. The height of the pebble after $t$ seconds is given by the equation $h=-16t^2+25t+104$. How long after the pebble is thrown will it be 52 feet from the ground? Round to the nearest tenth of a second.
}
{
	\begin{tabular}{l r}
	$52=-16t^2+25t+104$ or $0=-16t^2+25t+52$ & 1 pt to here\\
	$t=\frac{-25 \pm \sqrt{25^2-4(-16)(52)}}{2(-16)}$ & 2 pt to here\\
	$t=2.74602$ &  3 pts to here\\
	$2.7$ seconds & 4 pts to here\\
	\end{tabular}
}

\newproblem{16.5c}
{
	The Wollombi Falls in Australia have a height of 1100 feet. A pebble is thrown upward from the top of the falls with an initial velocity of 30 feet per second. The height of the pebble after $t$ seconds is given by the equation $h=-16t^2+30t+1100$. How long after the pebble is thrown will it be 550 feet from the ground? Round to the nearest tenth of a second.
}
{
	\begin{tabular}{l r}
	$550=-16t^2+30t+1100$ or $0=-16t^2+30t+550$ & 1 pt to here\\
	$t=\frac{-30 \pm \sqrt{30^2-4(-16)(550)}}{2(-16)}$ & 2 pt to here\\
	$t=6.875$ &  3 pts to here\\
	$6.9$ seconds & 4 pts to here\\
	\end{tabular}
}

\newproblem{16.5d}
{
	Victoria Falls in Zimbabwe have a height of 354 feet. A pebble is thrown upward from the top of the falls with an initial velocity of 40 feet per second. The height of the pebble after $t$ seconds is given by the equation $h=-16t^2+40t+354$. How long after the pebble is thrown will it be 177 feet from the ground? Round to the nearest tenth of a second.
}
{
	\begin{tabular}{l r}
	$177=-16t^2+40t+354$ or $0=-16t^2+40t+177$ & 1 pt to here\\
	$t=\frac{-40 \pm \sqrt{40^2-4(-16)(177)}}{2(-16)}$ & 2 pt to here\\
	$t=4.80316$ &  3 pts to here\\
	$4.8$ seconds & 4 pts to here\\
	\end{tabular}
}
