\newproblem{14.7a}
{
	The weight of an astronaut varies inversely as the square of his distance from the center of Earth. An astronaut weighs 112 pounds when he is 5000 miles from the center of Earth.
	\begin{enumerate}
	\item Write an equation relating the astronaut's weight to his distance from the center of Earth.
	\item Find the weight of the astronaut at 20000 miles from the center of Earth.
	\end{enumerate}
}
{
	\begin{tabular}{l r}
	(a) $W = \frac{k}{d^2}$ (or other variables) &  2 pts to here\\
	(a) $W=\frac{2800000000}{d^2}$ & 3 pts to here\\
	(b) $W = \frac{2800000000}{20000^2}$ or $C=7$ & 5 pts to here\\
	(b) $7$ pounds & 6 pts to here
	\end{tabular}
}

\newproblem{14.7b}
{
	If temperature remains constant, the volume of gas varies inversely as the pressure of the gas on its container. A pressure of 60 pounds per square inch corresponds to a volume of 45 cubic inches.
	\begin{enumerate}
	\item Write an equation relating pressure to volume.
	\item What pressure corresponds to a volume of 70 cubic inches?
	\end{enumerate}
}
{
	\begin{tabular}{l r}
	(a) $V = \frac{k}{P}$ (or other variables) & 2 pts to here\\
	(a) $V = \frac{2700}{P}$ & 3 pts to here\\
	(b) $V = \frac{2700}{100}$ or $C=27$ & 5 pts to here\\
	(b) $27$ pounds per square inch & 6 pts to here
	\end{tabular}
}

\newproblem{14.7c}
{
	The time it takes to fill a tub is inversely proportional to the square of the radius of the pipe used to fill it. When a pipe of radius 2.5 inches is used, the tub fills in 7.2 minutes. 
	\begin{enumerate}
	\item Write an equation relating the time it takes to fill the tub to the radius of the pipe used to fill it.
	\item Find the time to fill the tub using a pipe of radius 3.
	\end{enumerate}
}
{
	\begin{tabular}{l r}
	(a) $T = \frac{k}{r^2}$ (or other variables) & 2 pts to here\\
	(a) $T = \frac{45}{r^2}$ & 3 pts to here\\
	(b) $T = \frac{45}{9}$ or $C=5$ & 5 pts to here\\
	(b) $5$ minutes & 6 pts to here
	\end{tabular}
}

\newproblem{14.7d}
{
	The time it takes to get a sunburn is inversely proportional to the UV (ultraviolet) rating. At a UV rating of 6, it takes 15 minutes to get a sunburn.
	\begin{enumerate}
	\item Write an equation relating the time it takes to get a sumburn to the UV rating.
	\item Find the time it takes to get a sunburn when the UV rating is 10.
	\end{enumerate}
}
{
	\begin{tabular}{l r}
	(a) $T = \frac{k}{U}$ (or other variables) & 2 pts to here\\
	(a) $T = \frac{90}{U}$ & 3 pts to here\\
	(b) $T = \frac{90}{10}$ or $C=9$ & 5 pts to here\\
	(b) $9$ minutes & 6 pts to here
	\end{tabular}
}
