\newproblem{14.3a}
{
	The commission earned by a salesman varies directly as his gross sales. In one month, he earned a commission of $\$2,\!700$ on $\$18,\!000$ in gross sales. 
	\begin{enumerate}
	\item Write an equation relating the commission earned to the amount of gross sales in one month.
	\item Find the commission on $\$22,\!000$ in gross sales.
	\end{enumerate}
}
{
	\begin{tabular}{l r}
	(a) $C = ks$ (or other variables) & 2 pts to here\\
	(a) $C=\frac{2700}{18000}s$ or $C = \frac{3}{20}s$ & 3 pts to here\\
	(b) $C = \frac{3}{20}\cdot 22000$ or $C=3300$ & 5 pts to here\\
	(b) $\$3300$ & 6 pts to here
	\end{tabular}
}

\newproblem{14.3b}
{
	The number of AUD (Australian dollars) received varies directly as the number of USD (U.S. dollars) exchanged. In 2009, one could exchange 700 USD for 1085 AUD. 
	\begin{enumerate}
	\item Write an equation relating AUD to USD.
	\item In 2009, 1000 USD could be exchanged for how many AUD?
	\end{enumerate}
}
{
	\begin{tabular}{l r}
	(a) $A = kU$ (or other variables) & 2 pts to here\\
	(a) $A = \frac{1085}{700}U$ or $A = \frac{31}{20}U$ & 3 pts to here\\
	(b) $A = \frac{31}{20}\cdot 1000$ or $A=1550$ & 5 pts to here\\
	(b) $1550$ AUD & 6 pts to here
	\end{tabular}
}

\newproblem{14.3c}
{
	The volume of jet fuel used at cruising altitude by an MD80 passenger jet is directly proportional to time in flight. In flying at cruising altitude for 36 minutes, an MD80 uses 388 gallons of jet fuel.
	\begin{enumerate}
	\item Write an equation relating the amount of jet fuel used at cruising altitude to time at cruising altitude.
	\item Find the amount of jet fuel used by flying at cruising altitude for 90 minutes.
	\end{enumerate}
}
{
	\begin{tabular}{l r}
	(a) $V = kt$ & 2 pts to here\\
	(a) $V = \frac{388}{36}t$ or $V = \frac{97}{9}t$ & 3 pts to here\\
	(b) $V = \frac{97}{9}\cdot 90$ or $V=970$ & 5 pts to here\\
	(b) $970$ gallons & 6 pts to here
	\end{tabular}
}

\newproblem{14.3d}
{
	A patient has an insurance policy that requires a copayment that varies directly with her medical expenses. Her last bill listed her expenses at $\$1289$ with a copayment of $\$154.68$.
	\begin{enumerate}
	\item Write an equation relating her copayment to her medical expenses.
	\item Find her copayment for medical expenses totalling $\$2000$.
	\end{enumerate}
}
{
	\begin{tabular}{l r}
	(a) $c = km$ & 2 pts to here\\
	(a) $c = \frac{154.68}{1289}m$ or $c = 0.12m$ & 3 pts to here\\
	(b) $c = 0.12(2000)$ or $c=240$ & 5 pts to here\\
	(b) $\$240$ & 6 pts to here
	\end{tabular}
}
