\newproblem{17a}
{
	A brace for a shelf has the shape of a right triangle. Its hypotenuse is $10$ inches long and the two legs are equal in length. How long are the legs of the triangle? Keep answers in simplified radical form.
}
{
	\begin{tabular}{l r}
	$x^2+x^2 = 10^2$ & 1 pt to here\\
	$x^2=50$ & 2 pts to here\\
	$x=\sqrt{50}$ or $x=\pm \sqrt{50}$ & 3 pts to here\\
	$x=5\sqrt{2}$ in. & 4 pts to here (3 pts no units)
	\end{tabular}
}

\newproblem{17b}
{
	A monitor at Bulls-eye's electronics is listed as being 20 inches.  This distance is the diagonal 
distance across the screen  If the monitor has a square screen, what is the width of the screen?  Keep answers in simplified radical form.
}
{
	\begin{tabular}{l r}
	$x^2+x^2 = 20^2$ & 1 pt to here\\
	$x^2=200$ & 2 pts to here\\
	$x=\sqrt{200}$ or $x=\pm \sqrt{200}$ & 3 pts to here\\
	$x=10\sqrt{2}$ in. & 4 pts to here (3 pts no units)
	\end{tabular}
}

\newproblem{17c}
{
	Tanya runs diagonally across a square field, from corner to corner.  The total distance she ran was 40 yards.  What is the 
length of each side of the square field?  Keep answers in simplified radical form.
}
{
	\begin{tabular}{l r}
	$x^2+x^2 = 40^2$ & 1 pt to here\\
	$x^2=800$ & 2 pts to here\\
	$x=\sqrt{800}$ or $x=\pm \sqrt{800}$ & 3 pts to here\\
	$x=20\sqrt{2}$ yards & 4 pts to here (3 pts no units)
	\end{tabular}
}

\newproblem{17d}
{
	An 18-foot ladder is placed diagonally on a wall so that it forms an isosceles triangle with the wall and the ground.  This means the distance from the wall to the bottom of the ladder is the same as the distance from the bottom of the wall to the top of the ladder. What is the distance from the wall to the bottom of the ladder? Keep answers in simplified radical form.
}
{
	\begin{tabular}{l r}
	$x^2+x^2 = 18^2$ & 1 pt to here\\
	$x^2=162$ & 2 pts to here\\
	$x=\sqrt{162}$ or $x=\pm \sqrt{162}$ & 3 pts to here\\
	$x=9\sqrt{2}$ feet. & 4 pts to here (3 pts no units)
	\end{tabular}
}
